\section{Dwarf}
Dwarves do not have darkvision.
Instead they have:

\subparagraph{Echolocation}
You have blindsight out to 20 ft.
If you become deafened, you lose blindsight for as long as you are deafened.


\section{Elf}
Elves do not have darkvision.
Instead they have:

\subparagraph{Low-light vision}
You can see in dim light within 60 feet as if it were bright light.

\subparagraph{Aquatic native}
You have a swim speed equal to your walking speed.

\subsection{High elf}
These are called Star Elves within my setting.
Nothing mechanically changes about them.

\subsection{Dark Elf}
These are called Ash Elves in my setting.

You have the following trait:

\subparagraph{Heat vision}
You can see warm-blooded creatures within 100 feet regardless of illumination.


\section{Dragonborn}
Dragonborn do not exist on Døvvan.
Maybe some day.


\section{Half-Elf}
Elves diverged too far back in evolutionary history to allow interbreeding with any other race.
As such, no half-elves exist.


\section{Half-Orc}
These are flavored as Orcs.
You have the following trait:

\subparagraph{Ancestral Devotion}
Gain proficiency in one of Animal Handling, History, or Performance.


\section{Tiefling}
Tieflings are the results of curses placed upon a pregnant person.
This curse must be backed by a significant Aetheric power, like a god or demon.
As such they are extremely rare and their children, should they have any, are not affected by any of the changes that were applied to them through the curse.


\section{Gnome}
Gnomes do not have darkvision.
Instead they have:

\subparagraph{Low-light vision}
You can see in dim light within 60 feet as if it were bright light.
