\section{Bhan}
In the northern plains and forests, these giants thrive.

\subsection{Magical Adepts}
Bhain value shaping above all else.
They demonstrate their prowess to each other in two major ways: glamor and cold resistance.
They glamor themselves to be extremely beautiful, with prominent cheekbones and defined muscles.
They also wear almost no clothes despite the cold climate, relying instead on passively drawing in heat from their surroundings to keep them warm.


\subsection{Bhan Traits}
\subparagraph{Ability Score Increase}
Your Intelligence score increases by 2, and your Strength score increases by 1.

\subparagraph{Age}
Bhain commonly live to age 150, and max out around 200.
They have a long childhood and reach maturity around 25.

\subparagraph{Size}
Bhain stand around 8 to 9 feet tall.
Your size is Medium.

\subparagraph{Speed}
Your base walking speed is 30 feet.

\subparagraph{Languages}
You can speak Giant and Bhan.

\subparagraph{Powerful Build}
You count as one size larger when determining your carrying capacity and the weight you can push, drag, or lift.

\subparagraph{Glamor Mastery}
Through a lifetime of practice, you are able to cast \textit{Disguise Self} at will as a bonus action.

\subparagraph{Heat Exchange}
Your magic protects you from any environmental effects of excessive heat or cold.

\subparagraph{Magical Training}
You learn a cantrip of your choice.
You also learn a first-level spell from the wizard spell list and can cast it once per day without using a spell slot.
