\DndItemHeader{Knife Disk}{Wondrous item, common, consumable}
As an action, you can throw this glass disk at a point within 30 feet.
It explodes into countless fragments that fly out at high speeds in random directions.
All creatures within a 5-foot radius of that point must make a DC 13 Dexterity saving throw.
They take 4d4 slashing damage on a failure or half that on a success.

\DndItemHeader{Lighting Rod}{Wondrous item, common}
Once per day, you can use this rod to cast \textit{light} upon itself.

\DndItemHeader{Moth Cloak}{Wondrous item, rare}
This gnomish cloak is said to be made of the wings of hundreds of camouflaged moths.
It bends light to break up your silhouette.
This makes you able to hide while moving and to have advantage on stealth checks.
Only a few have been made for anyone not sized like a gnome.

\DndItemHeader{Bloodstone Ring}{Wondrous item, rarity varies}
Twice per day, you can use your action to cast either a life drain or a healing power using this ring.
Both effects count as spell attacks (using either Intelligence or your spellcasting ability) with a range of touch.
You must alternate between these effects.
%! suppress = EscapeAmpersand
\begin{DndTable}[header=Effect strength]{XXX}
    Rarity & Life drain & Healing \\
    Uncommon & 2d10 & 2d6 \\
    Rare & 4d10 & 3d8 \\
    Very Rare & 6d10 & 4d12
\end{DndTable}

\DndItemHeader{Vial of Healing}{Wondrous item, uncommon}
This small silver tube can hold a small mouthful of liquid.
It starts with 1d4 charges.
When liquid in this vial is drunk, it expends a charge to heal the drinker 2d4+2 hit points.
The vial can be refilled with any liquid you want and used again until it is out of charges.

\DndItemHeader{Torc of Terrifying Glamer}{Wondrous item, common}
This collar made of dzevv copper can project a monstrous illusion upon you when you activate it using an action.
While you have the illusion active, you gain advantage on Intimidation checks.

\DndItemHeader{Dzevv Iron Weapon}{Weapon (any metal, common)}
A weapon made with dzevv iron on its edges gives +1 to attack and damage rolls.
There are two major variants of these weapons.
The common variant have a core of normal flexible steel, with only the edges made of Dzevv iron.
The uncommon variant is made fully from dzevv iron, and is therefore cannot be targeted by magic.

\DndItemHeader{Dzevv Lead Armor}{Armor (any metal, rare)}
Dzevv lead absorbs magic.
It gives you a +1 bonus on saving throws to resist the effects of spells, and a +1 bonus to AC when being attacked with a spell.
It costs 500 gp more than its mundane counterpart, and weighs 1.5$\times$ as much.

Full plate is an exception.
Its cost is instead doubled.
It gives you advantage on saving throws to resist the effects of spells, and when you are attacked using a spell the attacker has disadvantage.

\DndItemHeader{Tailwind Pendant}{Wondrous item, common}
Once per day, you can cast \textit{expeditious retreat} upon yourself using this pendant.

\DndItemHeader{Sprouting Shield}{Armor (shield), common}
Once per day, as a reaction, you can cause woody roots to spring from this round wooden shield and entangle an attacker.
Use this when an enemy misses you with a melee attack.
That enemy becomes grappled by you.
On subsequent turns they can make the standard opposed roll to free themselves.

\DndItemHeader{Hammer Fist}{Armor (gauntlet), rare}
While wearing these gauntlets, you have proficiency in unarmed strikes and can make one as a bonus action on your turn as long as at least one of your hands is able to move.
Your unarmed strike counts as a magic weapon, has +1 to attack and damage rolls, and deals 1d4 base damage.

\DndItemHeader{Firestriker}{Wondrous item, common}
Using this item you can cast \textit{create bonfire} at will, except with a range of 10 feet.
Alternately, you can ignite any flammable material within the same range.
