\section{Selkie}
Like all shapechanger and hybrid species, they were created by magical means since the Awakening.
They were sourced from the humans of northwestern Jörðin where the cold currents leave the land arid and require the people to live off the sea.
The initial population was able to procreate and has maintained a stable population on Jörðin but have also taken to Kiyansi since contact.

Selkies have large eyes, with very dark sclera.

\subsection{Reclusive Hunters}
Selkies are most at home in the sea. 
They set up small villages along the coastline to return to after a successful hunt.
These villages mostly hold the men, as the women spend much of their time hunting.
More women are born than men, at a rate of about 2:1.
Their societies are matriarchal, and open relationships are the norm.
When a child is born, the mother and father raise it until weaning with the support of the clan. 
Then the father is left to be primary caregiver while the mother hunts.
The men tend toward crafting.


\subsection{Selkie Traits}

\subparagraph{Ability Score Increase}
Your Dexterity score increases by 2, and your Wisdom score increases by 1.

\subparagraph{Age}
Selkies live as long as humans do.

\subparagraph{Size}
In their humanoid form, they are like humans though tend to be shorter and rounder.
Your size is Medium.

\subparagraph{Speed}
When in humanoid form, you have a walking speed of 30 feet.

\subparagraph{Low-light Vision}
Your large eyes give you the ability to see unafflicted in dim light.

\subparagraph{Cold Insensitivity}
Due to your far Northern origins and a biology adapted to freezing water, you have resistance to cold damage and suffer no ill effects from cold temperatures.

\subparagraph{Languages}
You can speak Human and Selkie.

\subparagraph{Seal Skin}
As an action, you can transform into a seal.
Use the rules for the Druid's \textit{Wild Shape} ability, with the modification that you can stay in seal form indefinitely.
In your seal form, you can speak a reduced form of Selkie, suitable for simple commands and warnings.

\begin{DndMonster}{Seal}
    \DndMonsterType{Medium beast, neutral}
    \DndMonsterBasics[
        armor-class=12,
        hit-points=\DndDice{3d8+3},
        speed={10 ft., swim 60 ft.},
    ]
    \DndMonsterAbilityScores[
        str = 16,
        dex = 14,
        con = 13,
        int = 4,
        wis = 13,
        cha = 8,
    ]
    \DndMonsterDetails[
        challenge=1/2,
        damage-resistances=Cold
    ]

    \DndMonsterAction{Hold Breath}
    The seal can hold its breath for 30 minutes.

    \DndMonsterSection{Actions}
    \DndMonsterAttack[
        name=Bite,
        distance=melee,
        mod=+3,
        dmg=\DndDice{2d6+3},
        dmg-type=piercing,
    ]
\end{DndMonster}
